Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2025-02-17 src/tex/ms.tex
[showyourwork] overleaf sync

   \author{Tobias Buck\inst{1,2}
          \and
          Berkay Günes\inst{1,2}
          \and
          et al.
          }

@@

We use a NPE \cite{zeghal2022neuralposteriorestimationdifferentiable} which utilises the gradients of the generative model $\mathcal{M}$ with a Neural Spline Flow (NSF) \citet{durkan2019neuralsplineflows} containing 20 hidden features and 10 transformation layers for the normalizing flow. The NSF uses as invertible transformation smooth and flexible spline functions to allow efficient sampling. The expressivity of the spline allows the NDE to be capture complex distributions, while also maintaining computational tractability. The final model was selected after extensive hyperparameter tuning, varying: the architecture between NSF, Masked Autoregressive Flow (MAF) \cite{papamakarios2018maskedautoregressiveflowdensity}, and Mask Autoregressive 
Flow with rational-quadratic spline (MAF-RQS), the number of neurons between {10, 20, 50, 100}, and the number of transformations between {1, 5, 10, 30}, optimizing over the test set for both the highest mean log posterior probability and the best calibration as measured by the TARP value \citep{Lemos2023}. For more details on TARP see \ref{sec:sbc} in the appendix.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/Nstar_comp_different_prior.pdf}
    \vspace{-.5cm}
    \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for mock data a created with parameters for $\alpha_{IMF}$ and $\log_{10}(N_{Ia})$.}
    \label{fig:N_star_analysis_different_prior}
    \script{additional_inference.py}
\end{figure*}
\end{appendix}

>>>>

   \author{Tobias Buck\inst{1,2}
          \and
          Berkay Günes\inst{1,2}
          \and
          Giuseppe Viterbo\inst{1,2}
          \and
          William H. Oliver\inst{1,2}
          \and
          et al.
          }

@@

We use a NPE \cite{zeghal2022neuralposteriorestimationdifferentiable} which utilises the gradients of the generative model $\mathcal{M}$ with a Neural Spline Flow (NSF) \citet{durkan2019neuralsplineflows} containing 20 hidden features and 10 transformation layers for the normalizing flow. The NSF uses as invertible transformation smooth and flexible spline functions to allow efficient sampling. The expressivity of the spline allows the NDE to be capture complex distributions, while also maintaining computational tractability. The final model was selected after extensive hyperparameter tuning, varying: the architecture between NSF, Masked Autoregressive Flow (MAF) \cite{papamakarios2018maskedautoregressiveflowdensity}, and Mask Autoregressive 
Flow with rational-quadratic spline (MAF-RQS), the number of neurons between {10, 20, 50, 100}, and the number of transformations between {1, 5, 10, 30}, optimizing over the test set for both the highest mean log posterior probability and the best calibration as measured by the TARP value \citep{Lemos2023}. For more details on the TARP value see section \ref{sec:sbc} in the appendix.

@@

% \begin{figure*}
%     \centering
%     \includegraphics[width=\textwidth]{figures/Nstar_comp_different_prior.pdf}
%     \vspace{-.5cm}
%     \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for mock data a created with parameters for $\alpha_{IMF}$ and $\log_{10}(N_{Ia})$.}
%     \label{fig:N_star_analysis_different_prior}
%     \script{additional_inference.py}
% \end{figure*}

\end{appendix}
